### 2020-04-30 final_report/data.tex
remove negative space from wrapped figures
improve typesetting

\begin{wrapfigure}{r}{0.5\textwidth}
  \vspace{-30pt}
  \begin{center}
    \hspace*{-.3\columnsep}\includegraphics[width=0.58\textwidth]{fig3_allvar.jpg}
	\caption{Semivariograms for MC TBR data with coolant materials: (a) \ce{He},
	(b) \ce{H2O}, (c) \ce{D2O}}
    \label{fig:var}
  \end{center}
  \vspace{-50pt}
\end{wrapfigure}

@@

\begin{wrapfigure}{r}{0.25\textwidth}
	\centering
	\vspace{-5ex}
	{\footnotesize \incfigscale{0.8}{autoencoder}}
	\caption{Autoencoder with input width~$W_0$ and bottleneck width~$W_1$.
	Here, $\text{Dense}(N)$ denotes a fully-connected layer of $N$ neurons.}
	\label{fig:autoencoder}
	\vspace{-9ex}
\end{wrapfigure}

@@

In particular, we consider two equally-sized sets\footnote{Each set contained
\num{100000}~samples from batches 0-99 of the corresponding runs.} of samples: (i) a subset of data obtained
from run~1 and (ii) a subset of a single slice obtained from run~2. Our
expectation was that while the former case would provide meaningful insights into
correlations within the feature space, the latter would validate our
autoencoder implementation by analysing a set of points that are trivially
reducible in dimensionality due to a number of fixed discrete features.

\begin{wrapfigure}{r}{0.4\textwidth} % TODO: regenerate both plots as described
	\centering
	\vspace{-1ex}
	\begin{subfigure}[b]{\linewidth}
		\includegraphics[width=\linewidth,trim={0 48px 0 0},clip]{ae_mixed}
	\end{subfigure}

@@

	\caption{Autoencoder loss scan on the full feature space (top) and a single slice
		(bottom). Dimensional reduction is indicated by a green arrow.}
	\label{fig:autoencoder-loss}
	\vspace{-10ex}
\end{wrapfigure}

>>>>

\begin{wrapfigure}[30]{r}{0.5\textwidth}
	\centering
	\hspace*{-.3\columnsep}\includegraphics[width=0.58\textwidth]{fig3_allvar.jpg}
	\caption{Semivariograms for MC TBR data with coolant materials: (a) \ce{He},
	(b) \ce{H2O}, (c) \ce{D2O}}
	\label{fig:var}
\end{wrapfigure}

@@

@@

\begin{wrapfigure}[15]{l}{0.25\textwidth}
	\centering
	{\footnotesize \incfigscale{0.8}{autoencoder}}
	\caption{Autoencoder with input width~$W_0$ and bottleneck width~$W_1$.
	Here, $\text{Dense}(N)$ denotes a fully-connected layer of $N$ neurons.}
	\label{fig:autoencoder}
\end{wrapfigure}

In particular, we consider two equally-sized sets\footnote{Each set contained
\num{100000}~samples from batches 0-99 of the corresponding runs.} of samples:
(i)~a subset of data obtained
from run~1 and (ii)~a subset of a single slice obtained from run~2. Our
expectation was that while the former case would provide meaningful insights into
correlations within the feature space, the latter would validate our
autoencoder implementation by analysing a set of points that are trivially
reducible in dimensionality due to a number of fixed discrete features.

\begin{wrapfigure}[22]{r}{0.4\textwidth}
	\centering
	\vspace{-4ex}

	\begin{subfigure}[b]{\linewidth}
		\includegraphics[width=\linewidth,trim={0 48px 0 0},clip]{ae_mixed}
	\end{subfigure}

@@

	\caption{Autoencoder loss scan on the full feature space (top) and a single slice
		(bottom). Dimensional reduction is indicated by a green arrow.}
	\label{fig:autoencoder-loss}
\end{wrapfigure}
